Cover letter for the IJRR submission \\ ``An efficient acyclic contact planner for multiped robots''

### 2017-01-20 cover2.tex
cosmetics

\section{Originality and interest of the work}
We strongly disagree with reviewer 2 regarding the originality of the work. Reviewer 1 states that we simply experiment with minor heuristic adjustments.
Bretl formalized well the problem without providing an algorithm applicable to the general case. Escande focused on the contact planning $\mathcal{P}_2$. 
Our work tackles $\mathcal{P}_1$ as well, in a much more efficient manner than Bouyarmane et al.. 
These works, including the one of Hauser, are limited by the computational complexity of considering the full dimension of the problem.

@@

\section{On the static equilibrium of each configuration}
Reviewer 1 stated that ``the planned contact path is only discrete with static equilibrium considered for each
configuration, which is not very realistic''. First, we recall that this assumption is always made in the previous works that address cluttered scenarios,
such as the work from Bretl and Escande. Works that do not make this assumption such as Mordatch and al. only offer local convergence and can't address these scenarios. Furthermore, this limitation is in fact less restrictive in our approach that the one of Escande, since while our plan is quasi static, our resulting motion is dynamic, as now explained in the paper (Section 5.1).

>>>>

\section{Originality and interest of the work}
We strongly disagree with reviewer 2 regarding the originality of the work when he states that we simply ``\textit{experiment with minor heuristic adjustments}''.
Bretl formalized well the problem without providing an algorithm applicable to the general case. Escande focused on the contact planning $\mathcal{P}_2$. 
Our work tackles $\mathcal{P}_1$ as well, in a much more efficient manner than Bouyarmane et al.. 
These works, including the one of Hauser, are limited by the computational complexity of considering the full dimension of the problem.

@@

\section{On the static equilibrium of each configuration}
Reviewer 1 stated that ``\textit{the planned contact path is only discrete with static equilibrium considered for each
configuration, which is not very realistic''}. While we agree with the observation, we first recall that this assumption is made in the previous works that address cluttered scenarios, such as the work from Bretl and Escande. Works that do not make this assumption such as Mordatch and al. only offer local convergence and can't address these scenarios. Furthermore, this limitation is in fact less restrictive in our approach that the one of Escande, since while our plan is quasi static, our resulting motion is dynamic, as now explained in the paper (Section 5.1).
